\chapter{State of the Art}

In this chapter is an overview of the state-of-the art for this thesis. The common research field is computer vision. State-of-the-art presents the results of recent publications but since numbers alone are not meaningful, the methods and the exact context are also discussed. This includes approaches based on deep unsupervised metric learning , graph theory and data argumentation. 

Puzzling and information retrieval from historical documents is becoming increasingly popular in the computer vision community. The applications, challenges and projects focus on different areas. The diagram in Figure X is a chronological overview of research areas and state-of-the art publications. The areas are not defined in a general way. The publications were choosen subjectivly by us. The are just a subset of all the work and include just the state-of-the art.

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}


\resizebox{\textwidth}{!}{
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|}
	\hline
	\textbf{Task} & \textbf{Publication} & \textbf{Year} & \textbf{Method} & \textbf{Dataset} & \textbf{Public} & \textbf{Train Data} & \textbf{Val Data} & \textbf{Test Data} & \textbf{Metric} & \textbf{Result} \\ \hline
	\begin{tabular}[c]{@{}l@{}}Fragment\\ Retrieval\end{tabular} & \begin{tabular}[c]{@{}l@{}}Self-supervised\\ deep metric learning\\  for ancient papyrus\\ fragments retrieval\end{tabular} & 2021 & \begin{tabular}[c]{@{}l@{}}Self-supervised\\ deep metric\\ learning\end{tabular} & Michigan & yes & 800 papyri & 100 papyri & 100 papyri & \begin{tabular}[c]{@{}l@{}}Top-1\\ Accuracy\end{tabular} & 0.73 \\ \hline
	\begin{tabular}[c]{@{}l@{}}Fragment\\ Retrieval\end{tabular} & \begin{tabular}[c]{@{}l@{}}Self-supervised deep\\ metric learning for\\ ancient papyrus\\ fragments retrieval\end{tabular} & 2021 & \begin{tabular}[c]{@{}l@{}}Self-supervised\\ deep\\ metric\\ learning\end{tabular} & Hisfrag & yes & 9000 papyri & 1000 papyri & 100 papyri & \begin{tabular}[c]{@{}l@{}}Top-1\\ Accuracy\end{tabular} & 0.87 \\ \hline
	\begin{tabular}[c]{@{}l@{}}Fragment\\ Retrieval\end{tabular} & \begin{tabular}[c]{@{}l@{}}Papy-S-Net: A \\ Siamese Network\\ to match \\ papyrus fragments\end{tabular} & 2019 & \begin{tabular}[c]{@{}l@{}}Siamese\\ Network\end{tabular} & B500 & no & 8500 patches & 2000 patches & \begin{tabular}[c]{@{}l@{}}1000 patches\\ (~50 fragments)\end{tabular} & \begin{tabular}[c]{@{}l@{}}True Pos. /\\ Accuracy\end{tabular} & 0,79 \\ \hline
	\begin{tabular}[c]{@{}l@{}}Position\\ Estimation\end{tabular} & \begin{tabular}[c]{@{}l@{}}Using Graph Neural\\ Networks to Reconstruct\\ Ancient Documents\end{tabular} & 2021 & \begin{tabular}[c]{@{}l@{}}Graph\\ Neural\\ Networks\end{tabular} & \begin{tabular}[c]{@{}l@{}}B500\\ (subset)\end{tabular} & no & 3394 imgs & 500 images & 200 images & Accuracy & 0.85 \\ \hline
	\begin{tabular}[c]{@{}l@{}}Data\\ Argumen-\\ tation\end{tabular} & \begin{tabular}[c]{@{}l@{}}Data Augmentation\\ Generative Adversarial\\ Networks\end{tabular} & 2018 & \begin{tabular}[c]{@{}l@{}}Generative\\ Advesarial\\ Networks\end{tabular} & EMNIST & yes & - & - & - & Accuracy & +0.13 \\ \hline
\end{tabular}}

\section{Deep Metric Learning}
As indicated in the introduction, DML is a comparison-based algorithm and is therefore well suited for a field in which there is little ground truth. Pirone and his colleagues were the first who used DML in domain of papyri fragment retrieval. In their 2019 paper "Papy-S-Net : A Siamese Network to match papyrus fragments", they presented a so-called Siamese network that was able to correctly match 79\% of the papyri fragments. In 2021, they further improved their approach. A dataset under a public domain was generated to better evaluate their results. Through certain experiments with different models and preprocessing steps, a top-1 accuracy of 0.73\% was achieved. Because the authors communicated clearly what data was used, how it was prepared, and what metrics were used, the results from 2021 are much more reliable.


